When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-09-26 doc/paper/vpd_et_paper.tex
added vpd dependence plot to paper

>>>>

An additional concern is that the LAI term may in fact be some function of $D$, in which case the dependence would need to be accounted for when taking the derivative. Figure \ref{lai_vpd_fig} plots the jount distrivution of LAI and VPD, and shows that LAI is very weakly a function of VPD. Given this weak dependence, we argue that Equation \ref{d_et} is a valid approxiamtion for ET response to $D$.

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig03.png}
\caption{The joint distribution of $D$ and LAI. LAI has only a weak dependence on $D$}
\label{lai_vpd_fig}
\end{figure}

Before diving into calcualted values of $\frac{\partial \; ET}{\partial \; D}$, it is useful to consider the functional form of Equation \ref{d_et}. There are three terms: a scaling term for the full expression we will call Term 1 ($\frac{g_a \; P}{T(\Delta + \gamma)}$), a relatively constant offset we will call Term 2 ($\frac{c_p}{R_{air}}$), and a variable term we will call Term 3 ($- \frac{\gamma c_s }{\text{LAI }1.6 \; R\; \text{ uWUE }} \left( \frac{2 g_1 + \sqrt{D}}{2 (g_1 + \sqrt{D})^2}\right)$). All variables are constant, so the relative magnitude between Term 2 and Term 3 will determine the sign of the derivative, while Term 1 will scale the expression larger or smaller.
